---
title: "FrequencyFinder3"
output: html_document
date: "2026-05-23"
---

# Setup

## Clean Environment

```{r}
# List of items, mostly large things that are annoying to reinitialise
keep <- c("gtfs_tram") 
# Remove everything that is not in the keep list
rm(list = setdiff(ls(), keep))
# Get rid of everything if needed
#rm(list = ls())
```

## Load Libraries

```{r}
library(dplyr)
library(ggplot2)
library(data.table)
library(sf)
library(lwgeom)
library(leaflet)
library(leaflet.extras)
library(shiny)
library(jsonlite)
library(gtfstools)
library(vicgtfstools) # My own repo https://github.com/adambain014/vicgtfstools 
library(tictoc) # For my own benchmarking enjoyment
```

## Initialise the GTFS

```{r}
# Download the latest vic gtfs feed
if(!dir.exists("Temps/gtfs")){
  download_latest_vic_gtfs("Temps/gtfs")
}

# Open the tram GTFS
if(!exists("gtfs_tram")){
  gtfs_tram <- open_vic_gtfs("Temps/gtfs", "Metro_Tram")
}
```

## Create a stop times sorted by day and route
```{r}
refine_stop_times <- function(gtfs, target_day, target_route){

  # Find all service_ids active on the target day
  possible_service_ids <- gtfs$calendar[get(target_day) == 1, service_id]

  # Pick the service_id with the MOST trips for this route on this day
  # (more reliable than fewest calendar_dates exceptions)
  route_ids <- gtfs$routes[route_short_name == target_route, route_id]
  
  candidate_trips <- gtfs$trips[
    route_id %chin% route_ids & service_id %chin% possible_service_ids
  ]
  
  if(nrow(candidate_trips) == 0L)
    stop("No trips found for route ", target_route, " on ", target_day)
  
  service_ids <- candidate_trips[, .N, by = service_id][order(-N)][1, service_id]
  # Get route_id(s) for the target route_short_name
  route_ids <- gtfs$routes[route_short_name == target_route, route_id]

  # Get trip_ids for that route + canonical service_id
  trip_ids <- gtfs$trips[
    route_id %chin% route_ids & service_id %chin% service_ids,
    trip_id
  ]

  #  Filter stop_times by the trip_ids
  stop_times <- gtfs$stop_times[trip_id %chin% trip_ids]

  # Keep only needed columns
  cols_to_keep <- c(
    "trip_id",
    "departure_time",
    "stop_id",
    "stop_sequence",
    "shape_dist_traveled"
  )
  stop_times <- stop_times[, ..cols_to_keep]
  
  # Add direction_id
  direction_ids <- gtfs$trips[trip_id %chin% trip_ids, .(trip_id, direction_id)]
  stop_times <- stop_times[direction_ids, on = "trip_id"]
  
  # Turn departure times into seconds
  departure_times_to_minutes <- function(dt) {
    dt <- copy(dt)
    dt[, c("h","m","s") := tstrsplit(departure_time, ":", type.convert = TRUE)]
    dt[, departure_time_m := round(h*60 + m + s/60)]
    dt[, !c("h","m","s")]
  }

  stop_times <- departure_times_to_minutes(stop_times)

  return(stop_times)
}
```

# Summary Stats
Average Frequency for Morning, Daytime, and Evening across Monday, Saturday and Sunday
```{r}
# Function to add minutes until next service in same direction at same stop
time_until_next_service <- function(stop_times){
  
  waits <- copy(stop_times)
  
  # Sort to ensure correct order
  setorder(waits, stop_id, direction_id, departure_time_m)
  
  waits[,
    next_time_m := shift(departure_time_m, 1L, type = "lead"),
    by = .(stop_id, direction_id)
  ]
  
  # Drop last departure per group (no next service) — NAs now land correctly
  waits <- waits[!is.na(next_time_m)]
  
  waits[, wait_m := next_time_m - departure_time_m]
  
  return(waits)
}

freq_at_window <- function(waits, start_min, end_min) {
  window_waits <- waits[departure_time_m >= start_min & departure_time_m < end_min]
  
  if (nrow(window_waits) == 0) return(NA_real_)
  
  # Mean wait per stop+direction, then average across all stop+direction combos
  mean_wait <- window_waits[, .(mean_wait = mean(wait_m)), 
                              by = .(stop_id, direction_id)][, mean(mean_wait)]
  
  # Round to nearest 0.5
  mean_wait <- round(mean_wait*2)/2
  
  return(mean_wait)
}

# Function to derive wait times
freq_at_3_windows <- function(waits){

  morning <- freq_at_window(waits, 7 * 60, 8 * 60)
  daytime <- freq_at_window(waits, 12 * 60, 13 * 60)
  evening <- freq_at_window(waits, 21 * 60, 22 * 60)

  out <- data.table(morning = morning,
                    daytime = daytime,
                    evening = evening)
  }

# Test usage
stop_times_monday   <- refine_stop_times(gtfs_tram, "monday", "19")
stop_times_saturday <- refine_stop_times(gtfs_tram, "saturday", "19")
stop_times_sunday   <- refine_stop_times(gtfs_tram, "sunday", "19")

waits_monday   <- time_until_next_service(stop_times_monday)
waits_saturday <- time_until_next_service(stop_times_saturday)
waits_sunday   <- time_until_next_service(stop_times_sunday)

freq_monday   <- freq_at_3_windows(waits_monday)[, day := "Monday"]
freq_saturday <- freq_at_3_windows(waits_saturday)[, day := "Saturday"]
freq_sunday   <- freq_at_3_windows(waits_sunday)[, day := "Sunday"]

frequency_summary <- rbind(freq_monday, freq_saturday, freq_sunday) |>
  setcolorder("day", 1)
```

Peak medians
```{r}
peak_median <- function(waits, AMPM) {
  
  if (AMPM == "AM") {
    start_min <- 7 * 60   # 6:00
    end_min   <- 9 * 60   # 9:00
  }
  
  if (AMPM == "PM") {
    start_min <- 16 * 60  # 4:00 PM
    end_min   <- 19 * 60  # 7:00 PM
  }
  
  # Filter to the peak window
  window <- waits[
    departure_time_m >= start_min &
    departure_time_m <  end_min
  ]
  
  if (nrow(window) == 0) return(NA_real_)
  
  median(window$wait_m)
}

take_peak_medians <- function(waits){
  
  peak_medians <- data.table(`Median AM Peak Wait` = peak_median(waits, "AM"),
                             `Median PM Peak Wait` = peak_median(waits, "PM"))
  
  return(peak_medians)
}

# Test usage
stop_times_monday   <- refine_stop_times(gtfs_tram, "monday", "19")
waits_monday        <- time_until_next_service(stop_times_monday)
peak_medians        <- take_peak_medians(waits_monday)
```

Span stats
From Monday - Friday - Saturday - Sunday to pick up night network

```{r}
# Create a function to make a big unified stop times block across week
unified_stop_times <- function(gtfs, target_route){
  
  stop_times_monday    <- refine_stop_times(gtfs, "monday",    target_route)[,day := 1]
  stop_times_tuesday   <- refine_stop_times(gtfs, "tuesday",   target_route)[,day := 2]
  stop_times_wednesday <- refine_stop_times(gtfs, "wednesday", target_route)[,day := 3]
  stop_times_thursday  <- refine_stop_times(gtfs, "thursday",  target_route)[,day := 4]
  stop_times_friday    <- refine_stop_times(gtfs, "friday",    target_route)[,day := 5]
  stop_times_saturday  <- refine_stop_times(gtfs, "saturday",  target_route)[,day := 6]
  stop_times_sunday    <- refine_stop_times(gtfs, "sunday",    target_route)[,day := 7]
  
  stop_times_all <- rbind(stop_times_monday, 
                          stop_times_tuesday, 
                          stop_times_wednesday, 
                          stop_times_thursday, 
                          stop_times_friday, 
                          stop_times_saturday, 
                          stop_times_sunday)
  
  # Mark for past midnight
  stop_times_all <- stop_times_all[,past_midnight := departure_time_m >= 24 * 60]
  # Move to the next day
  stop_times_all <- stop_times_all[past_midnight == TRUE, day := day + 1]
  stop_times_all <- stop_times_all[day == 8, day := 1]
  # Change 25 to 1 etc.
  stop_times_all <- stop_times_all[past_midnight == TRUE, departure_time_m := departure_time_m - 24 * 60]
  
  return(stop_times_all)
}

# Function to break one day into spans
one_day_span <- function(unified_stop_times_o, target_day_number){
  
  day_stop_times <- unified_stop_times_o[day == target_day_number]
  
  valid_stops <- day_stop_times[,.N, by = "stop_id"][,pc_max := N / max(N)][pc_max > 0.1]$stop_id
  
  day_stop_times <- day_stop_times[stop_id %chin% valid_stops]
  
  day_stop_times_arranged <- day_stop_times[order(departure_time_m),.(departure_time_m, stop_id, past_midnight)]
  day_stop_times_arranged <- unique(day_stop_times_arranged)
  
  # find if there is a post midnight segment
  midnight_segment <- any(day_stop_times_arranged$past_midnight)
  
  # find if there is any gap
  day_stop_times_arranged_gap <- copy(day_stop_times_arranged)
  
  day_stop_times_arranged_gap[
    ,
    next_time_m := data.table::shift(departure_time_m, type = "lead")
  ]
  
  day_stop_times_arranged_gap[
    ,
    gap := next_time_m - departure_time_m
  ]
  
  is_gap <- max(day_stop_times_arranged_gap$gap, na.rm = TRUE) >= 2 * 60
  gap_row <- which.max(day_stop_times_arranged_gap$gap)
  
  #----#

  if (!midnight_segment) {
  
    span_start <- min(day_stop_times_arranged$departure_time_m)
    span_end   <- max(day_stop_times_arranged$departure_time_m)
  
    midnight_span_start <- NA_real_
    midnight_span_end   <- NA_real_
    
  
  } else if (is_gap) {
  
    span_start <- day_stop_times_arranged_gap$next_time_m[gap_row]
    span_end   <- 24 * 60
    
    midnight_span_start <- 0
    midnight_span_end   <- day_stop_times_arranged_gap$departure_time_m[gap_row]
    
  
  } else {
  
    span_start <- 0
    span_end   <- 24 * 60
  
    midnight_span_start <- NA_real_
    midnight_span_end   <- NA_real_

  }
  
  #----# Full coverage Version

  all_stop_ids <- unique(day_stop_times_arranged$stop_id)
  
  all_post_midnight_stop_ids <- unique(day_stop_times_arranged[past_midnight == TRUE]$stop_id)
  
  midnight_segment_coverage <- dplyr::setequal(all_stop_ids, all_post_midnight_stop_ids)
  
  # The concept here is to check if even if there is a midnight segment, maybe not all stops are in it.
  # If so then, the basic system shall happen
  
  past_midnight_times_earliest_finish <- 
  day_stop_times_arranged[past_midnight == TRUE, .(last_service = max(departure_time_m)), 
                           by = stop_id][, min(last_service)]

  day_midnight_latest_start <- 
    day_stop_times_arranged[past_midnight == FALSE, .(first_service = min(departure_time_m)), 
                             by = stop_id][, max(first_service)]
  
  is_coverage_gap <- day_midnight_latest_start - past_midnight_times_earliest_finish >= 2 * 60
  
  # The concept here is to find the first past midnight finish, and the latest day start, find out if there is a 2 hour gap between, and then initialise a boolean for the later if else else system
  
  #----#
  
  if (!midnight_segment_coverage) {
    day_only <- day_stop_times_arranged[past_midnight == FALSE]
      full_coverage_start <- day_only[, .(first_service = min(departure_time_m)), by = stop_id][, max(first_service)]
      full_coverage_end   <- day_only[, .(last_service  = max(departure_time_m)), by = stop_id][, min(last_service)]
  
    full_midnight_coverage_start <- NA_real_
    full_midnight_coverage_end   <- NA_real_
    
  
  } else if (is_coverage_gap) {
    
    full_coverage_start <- day_midnight_latest_start
    full_coverage_end   <- 24 * 60
    
    full_midnight_coverage_start <- 0
    full_midnight_coverage_end   <- past_midnight_times_earliest_finish
    
  
  } else {
  
    full_coverage_start <- 0
    full_coverage_end   <- 24 * 60
  
    full_midnight_coverage_start <- NA_real_
    full_midnight_coverage_end   <- NA_real_

  }

  #----#
  
  out <- data.table(
    day = target_day_number,
    span_start = span_start,
    span_end = span_end,
    midnight_span_start = midnight_span_start,
    midnight_span_end = midnight_span_end,
    full_coverage_start = full_coverage_start,
    full_coverage_end = full_coverage_end,
    full_coverage_midnight_start = full_midnight_coverage_start,
    full_coverage_midnight_end = full_midnight_coverage_end)
    
    return(out)
  
}


# Function to add span across the week

span_across_week <- function(unified_stop_times_o){
  
  monday_span    <- one_day_span(unified_stop_times_o, 1)[,day := "monday"]
  tuesday_span   <- one_day_span(unified_stop_times_o, 2)[,day := "tuesday"]
  wednesday_span <- one_day_span(unified_stop_times_o, 3)[,day := "wednesday"]
  thursday_span  <- one_day_span(unified_stop_times_o, 4)[,day := "thursday"]
  friday_span    <- one_day_span(unified_stop_times_o, 5)[,day := "friday"]
  saturday_span  <- one_day_span(unified_stop_times_o, 6)[,day := "saturday"]
  sunday_span    <- one_day_span(unified_stop_times_o, 7)[,day := "sunday"]
  
  out <- rbind(monday_span,
               tuesday_span,
               wednesday_span,
               thursday_span,
               friday_span,
               saturday_span,
               sunday_span)
  
  setcolorder(out, "day", 1)
  
  return(out)
}
  
# Test
week_stop_times <- unified_stop_times(gtfs_tram, "30")
span_summary <- span_across_week(week_stop_times)
```

# Example Plot
```{r}
plot_week_spans <- function(spans) {
  
  # Build long format for all days
  segments <- spans[, .(
    type  = c("Span", "Span (midnight)", "Full Coverage", "Full Coverage (midnight)"),
    start = c(span_start, midnight_span_start, full_coverage_start, full_coverage_midnight_start),
    end   = c(span_end,   midnight_span_end,   full_coverage_end,   full_coverage_midnight_end)
  ), by = day]
  
  # Drop NA rows
  segments <- segments[!is.na(start)]
  
  # Convert to hours
  segments[, start_h := start / 60]
  segments[, end_h   := end   / 60]
  
  # Collapse midnight into same type as its counterpart for colour
  segments[, type_colour := fcase(
    type %in% c("Span", "Span (midnight)"),             "Span",
    type %in% c("Full Coverage", "Full Coverage (midnight)"), "Full Coverage"
  )]
  
  # Order days
  day_levels <- c("monday","tuesday","wednesday","thursday","friday","saturday","sunday")
  day_labels <- c("Monday","Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday")
  segments[, day := factor(day, levels = day_levels, labels = day_labels)]
  
  ggplot(segments, aes(y = type_colour, colour = type_colour, group = type)) +
    geom_segment(aes(x = start_h, xend = end_h, yend = type_colour), linewidth = 4) +
    scale_x_continuous(
      breaks = seq(0, 24, by = 4),
      labels = function(x) sprintf("%02d:00", as.integer(x)),
      limits = c(0, 24)
    ) +
    scale_colour_manual(
      values = c("Span" = "#2196F3", "Full Coverage" = "#FF5722"),
      name   = NULL
    ) +
    facet_wrap(~ day, ncol = 1, strip.position = "left") +
    labs(
      title = "Service span across the week",
      x = NULL,
      y = NULL
    ) +
    theme_minimal() +
    theme(
      strip.text.y.left = element_text(angle = 0, hjust = 1),
      axis.text.y       = element_blank(),
      axis.ticks.y      = element_blank(),
      legend.position   = "bottom"
    )
}

# Usage
week_stop_times <- unified_stop_times(gtfs_tram, "11")
span_summary <- span_across_week(week_stop_times)
plot_week_spans(span_summary)
```

## Leaflet interactive
Split days into 30 min chunks across 7 days of the week, and assign a frequency to each "duplet"

First lets make duplet sfs

```{r}
build_stop_pair_shapes <- function(stop_times, gtfs) {
  
  # Get unique stop pairs with their two stop IDs
  duplets <- stop_times[, .SD[1], by = "stop_pair_id"][, .(stop_pair_id, stop_id, next_stop_id)]
  
  # Join coordinates for each stop
  stop_coords <- gtfs$stops[, .(stop_id, stop_lat, stop_lon)]
  
  duplets <- duplets[stop_coords, on = "stop_id", nomatch = 0]
  setnames(duplets, c("stop_lat", "stop_lon"), c("lat1", "lon1"))
  
  duplets <- duplets[stop_coords, on = c("next_stop_id" = "stop_id"), nomatch = 0]
  setnames(duplets, c("stop_lat", "stop_lon"), c("lat2", "lon2"))
  
  # Build straight-line geometries
  duplets_sf <- st_sf(
    stop_pair_id = duplets$stop_pair_id,
    geometry = st_sfc(
      mapply(function(lon1, lat1, lon2, lat2) {
        st_linestring(rbind(c(lon1, lat1), c(lon2, lat2)))
      }, duplets$lon1, duplets$lat1, duplets$lon2, duplets$lat2,
      SIMPLIFY = FALSE),
      crs = 4326
    )
  )
  
  return(duplets_sf)
}



stop_times_week <- unified_stop_times(gtfs_tram, 1)
stop_times <- stop_times_week[, next_stop_id := shift(stop_id, 1L, type = "lead"), by = .(trip_id)
                              ][, next_shape_dist_traveled := shift(shape_dist_traveled, 1L, type = "lead"), 
                                by = .(trip_id)
                              ][, stop_pair_id := paste0(stop_id, "-", next_stop_id)
                              ][order(trip_id, stop_sequence)
                              ][!is.na(next_stop_id)
                              ]

stop_pair_shapes <- build_stop_pair_shapes(stop_times, gtfs_tram)
```

Find out current wait period for each first stop of each duplet - at every 30 minute intervals 7 days a week
```{r}
add_first_30_next_day <- function(stop_times){
  extra_30 <- stop_times[departure_time_m < 30]
  
  extra_30[,departure_time_m := departure_time_m + 30 * 60]
  extra_30[,day := day - 1]
  extra_30[day == 0 ,day := 7]
  
  stop_times_added <- rbind(stop_times, extra_30)
}


get_day_waits <- function(stop_times, day_number){

  stop_times_i <- stop_times[day == day_number]
  
  stop_times_i <- stop_times_i[order(departure_time_m)]

  stop_times_i <- stop_times_i[
    ,
    next_departure_time_m := data.table::shift(departure_time_m, 1L, type = "lead"),
    by = stop_pair_id
  ][!is.na(next_departure_time_m)][,gap := next_departure_time_m - departure_time_m]

  stop_times_i <- stop_times_i[, .(stop_pair_id, direction_id, departure_time_m, next_departure_time_m, gap, day)]
  return(stop_times_i)
}


# Function to get the gap value that :00 or :30 falls on per stop_pair
get_30_minute_gap_snapshots_per_stop_id <- function(stop_times) {
  
  snapshots <- data.table(
    day        = rep(1:7, each = 48),
    snapshot_m = rep(seq(0, 23.5 * 60, by = 30), times = 7)
  )
  
  stop_times_waits <- rbindlist(lapply(1:7, get_day_waits, stop_times = stop_times))
  
  # Non-equi join: snapshot falls within [departure_time_m, next_departure_time_m)
  result <- stop_times_waits[
    snapshots,
    .(stop_pair_id, direction_id, day, snapshot_m = i.snapshot_m, gap),
    on = .(
      day                   == day,
      departure_time_m      <= snapshot_m,
      next_departure_time_m >  snapshot_m
    ),
    nomatch = 0
  ]
  # Round up to frequency group
  result[, gap_group := fcase(
  gap <= 10, 10,
  gap <= 15, 15,
  gap <= 20, 20,
  gap <= 30, 30,
  gap <= 60, 60,
  default   = NA_real_  # no service / very infrequent
)]
  
  return(result)
}


# test


stop_times_week <- unified_stop_times(gtfs_tram, 1)
stop_times <- stop_times_week[, next_stop_id := shift(stop_id, 1L, type = "lead"), by = .(trip_id)
                              ][, next_shape_dist_traveled := shift(shape_dist_traveled, 1L, type = "lead"), 
                                by = .(trip_id)
                              ][, stop_pair_id := paste0(stop_id, "-", next_stop_id)
                              ][order(trip_id, stop_sequence)
                              ][!is.na(next_stop_id)
                              ]

stop_times <- add_first_30_next_day(stop_times)
snapshots_waits <- get_30_minute_gap_snapshots_per_stop_id(stop_times)
```

GTFS (R pipeline)
   ↓
precomputed_data.json
   ↓
GitHub Pages frontend
   ↓
JS renders maps + charts



## Function to make json dataset for each route
```{r}
make_pre_json <- function(gtfs, route_number){
  
  # Get Colour
  colour <- gtfs$routes[route_short_name == route_number]$route_color[1]
  
  # Get destinations for directions
  route_destination_1 <- gtfs$trips[route_id %chin% gtfs$routes[route_short_name == route_number]
                                    ][direction_id == 1][,.N, by = "trip_headsign"][order(-N)
                                                                                    ][1]$trip_headsign
  route_destination_0 <- gtfs$trips[route_id %chin% gtfs$routes[route_short_name == route_number]
                                    ][direction_id == 0][,.N, by = "trip_headsign"][order(-N)
                                                                                    ][1]$trip_headsign

  # Frequency Summary
  stop_times_monday   <- refine_stop_times(gtfs, "monday", route_number)
  stop_times_saturday <- refine_stop_times(gtfs, "saturday", route_number)
  stop_times_sunday   <- refine_stop_times(gtfs, "sunday", route_number)

  waits_monday   <- time_until_next_service(stop_times_monday)
  waits_saturday <- time_until_next_service(stop_times_saturday)
  waits_sunday   <- time_until_next_service(stop_times_sunday)

  freq_monday   <- freq_at_3_windows(waits_monday)[, day := "Monday"]
  freq_saturday <- freq_at_3_windows(waits_saturday)[, day := "Saturday"]
  freq_sunday   <- freq_at_3_windows(waits_sunday)[, day := "Sunday"]

  frequency_summary <- rbind(freq_monday, freq_saturday, freq_sunday)

  # Peak Medians
  peak_medians <- take_peak_medians(waits_monday)
  
  # Span
  
  week_stop_times <- unified_stop_times(gtfs, route_number)
  span_summary <- span_across_week(week_stop_times)
  
  # Interactive
 stop_times <- week_stop_times[, next_stop_id := shift(stop_id, 1L, type = "lead"), by = .(trip_id)
                            ][, next_shape_dist_traveled := shift(shape_dist_traveled, 1L, type = "lead"), 
                              by = .(trip_id)
                            ][, stop_pair_id := paste0(stop_id, "-", next_stop_id)
                            ][order(trip_id, stop_sequence)
                            ][!is.na(next_stop_id)
                            ]

  stop_pair_shapes <- build_stop_pair_shapes(stop_times, gtfs_tram)
  stop_times <- add_first_30_next_day(stop_times)
  snapshots_waits <- get_30_minute_gap_snapshots_per_stop_id(stop_times)
  stop_pair_shapes <- stop_pair_shapes |>
    dplyr::left_join(snapshots_waits, by = "stop_pair_id")

  final_int <- as.data.table(stop_pair_shapes)[
      ,
      .(
        geometry = geometry[1],
        data = list(
          .(
            day          = day,
            snapshot_m   = snapshot_m,
            gap          = gap,
            gap_group    = gap_group,
            direction_id = direction_id
          )
        )
      ),
      by = stop_pair_id
    ]
    
  

  # FINAL STRUCTURE 
  out <- list(
    route_number = as.character(route_number),
    route_colour = as.character(colour),
    route_destination_1 = as.character(route_destination_1),
    route_destination_0 = as.character(route_destination_0),
    frequency_summary = as.data.frame(frequency_summary),
    peak_medians = as.data.frame(peak_medians),
    span_stats = as.data.frame(span_summary),
    interactive = as.data.frame(final_int)
  )

  return(out)
}

test <- make_pre_json(gtfs_tram, 48)

export_json <- function(gtfs, route_number){

  out <- make_pre_json(gtfs, route_number)

  path <- "route_jsons"

  if (!dir.exists(path)) {
    dir.create(path, recursive = TRUE)
  }

  jsonlite::write_json(
    out,
    path = file.path(path, paste0(route_number, ".json")),
    auto_unbox = TRUE,
    pretty = TRUE
  )

  invisible(out)
}

valid_routes <- gtfs_tram$routes$route_short_name |> unique()

lapply(valid_routes, function(r) export_json(gtfs_tram, r))

# Make a manifest
routes <- tools::file_path_sans_ext(list.files("route_jsons", pattern = "\\.json$"))
jsonlite::write_json(list(routes = setdiff(routes, "manifest")), "route_jsons/manifest.json", auto_unbox = TRUE)

```
